---
title: "How to create a qmd from gists"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create a qmd from gists}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bsu.tools)
```

Borrowing from the `rUM` package, the `new_quarto()` function enables you to 
create a new Quarto qmd file utilizing one of our built in templates.  

The function has three arguments:  
- filename: the name of your new file. If you forget the `.qmd` ending the 
function will automatically add it for you.  
- path: where should the file be created. Uses `here::here()` by default.  
- gist: the template you want to use (see below).  

As of `r Sys.Date()` there are currently 3 qmd gists available:   
- "no_logo_quarto",  
- "ctsc_quarto",  
- and "hac_quarto".  

Simply call `new_quarto(filename = "your-new-qmd", gist = "<one-of-the-three>")` 
in the console to create and open your new qmd file from the template.  

