---
title: "How to create project closeout documentation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create project closeout documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bsu.tools)
```

The `new_project_closeout()` function enables you to create a new Quarto document
for documenting project closeout information using a standardized template.

## Function Arguments

The function has two arguments:

- **filename**: the name of your new file. If you forget the `.qmd` ending the
function will automatically add it for you.
- **path**: where should the file be created. Uses `here::here()` by default.

## Template Sections

The project closeout template includes comprehensive sections for documenting
the completion of a research project:

- **Project Information**: Basic project details including title, investigators, and completion date
- **Project Summary**: Brief overview of research question, methods, and key findings
- **Final Data Files**: Table documenting raw data, processed data, and analysis datasets with their locations
- **Code and Analysis Files**: Table listing all scripts, code, and analysis files
- **Reports and Outputs**: Table of final reports and deliverables
- **Publications and Presentations**: Tables for manuscripts, conference presentations, and other dissemination
- **Project Collaborators**: List of all team members and their roles
- **Data Sharing and Reuse**: Information about data availability and sharing plans
- **Lessons Learned**: Documentation of challenges and recommendations
- **Project Closeout Checklist**: Checklist to ensure all closeout tasks are completed

## Usage

Simply call `new_project_closeout(filename = "project-name-closeout")` in the
console to create and open your new project closeout document from the template.

```{r, eval=FALSE}
# Create a new project closeout document
new_project_closeout(filename = "my-project-closeout")

# Create in a specific directory
new_project_closeout(filename = "my-project-closeout", path = "path/to/directory")
```

## Example Output

The template generates an HTML document with a table of contents and all the
structured sections needed to document project completion. The template includes
comprehensive tables for tracking final files (raw data, processed data, code/report)
and publications, with example entries that can be customized for your specific project.

## When to Use

Use this template when closing out a project to:

- Document the location of all final data files and code
- Track publications and presentations resulting from the project
- Create a comprehensive record for future reference
- Ensure all closeout tasks are completed
- Facilitate knowledge transfer and project archival
