---
title: "How to create project details documentation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to create project details documentation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bsu.tools)
```

The `new_project_details()` function enables you to create a new Quarto document
for documenting project details using a standardized template.

## Function Arguments

The function has two arguments:

- **filename**: the name of your new file. If you forget the `.qmd` ending the
function will automatically add it for you.
- **path**: where should the file be created. Uses `here::here()` by default.

## Template Sections

The project details template includes the following sections:

- **Investigator**: Information about the project investigator(s)
- **Research Question**: Description of the research question(s)
- **Hypothesis**: Statement of the project hypothesis or hypotheses
- **Statistical Analysis Plan**: Overview of statistical methods including primary analysis, secondary analysis, and sample size considerations
- **Timeline**: Table with project milestones and target dates
- **Project Outcome**: Expected deliverables and dissemination plans
- **Project Files**: Table documenting project files and their locations

## Usage

Simply call `new_project_details(filename = "project-name")` in the console to
create and open your new project details document from the template.

```{r, eval=FALSE}
# Create a new project details document
new_project_details(filename = "my-project-details")

# Create in a specific directory
new_project_details(filename = "my-project-details", path = "path/to/directory")
```

## Example Output

The template generates an HTML document with a table of contents and all the
structured sections needed to document your research project. The template
includes example tables for the timeline and project files that can be customized
to fit your specific needs.
