---
title: "Rmd-options-vignette"
output: 
  bookdown::html_document2: 
  base_format: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Rmd-options-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TestPackage)
```

# Rmarkdown 

Recommend having the output go to `html_document2` from the `bookdown` package (`output: bookdown::html_document2`). This will let you auto-number and cross-reference tables and figures.

## Chunk Options  

There are several options to control the display of Rmarkdown chunks and their output. A more detailed breakdown of chunk options can be found in the [R Markdown Cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html).

* echo: This controls the printing of the R code in the resulting HTML file. If `echo=TRUE` the code will be displayed in the output and if `echo=FALSE` the code will be suppressed in the output.

* eval: This controls whether or not the chunk is evaluated. If `eval=TRUE` the chunk will run and if `eval=FALSE` the chunk will not run.

* warning: This controls the printing of `warning` messages. If `warning=TRUE` the warning messages will be displayed and if `warning=FALSE` the warning messages will be suppressed. Recommend leaving `warning=TRUE` while working on the project and setting `warning=FALSE` before the final knit. 

* message: This controls the printing of messages. If `message=TRUE` the messages will be displayed and if `message=FALSE` the messages will be suppressed.

* include: Setting `include=FALSE` allows you to evaluate the chunk while suppressing all output (source code, warnings, message, text and figure output). 


## Using the Chunk Options within the Template  

One of the goals of the CTSC Template is to easily create an internal and external version of the report. To accomplish this the template has an `internal` variable that is set to `TRUE` by default. Use the `internal` variable to easily control the chunks depending on the recipient of the output. For the `asis` chunks that are used for additional text sections set `echo=internal`. To control code chunks set `include=interal` or `eval=internal` depending on whether or not you need that chunk to be evaluated.
