---
title: "Tables-Figures-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tables-Figures-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TestPackage)
```

# Tables

There are three packages I recommend for generating tables: `kableExtra`, `arsenal`, and `sjPlot`.

* `kable` from the `kableExtra` package for printing tables from data frames.
* `tableby` from the `arsenal` package for creating summary tables.
* `tab_model` from the `sjPlot` package for creating HTML tables with model results.  

We are currently aware of two packages that should be avoided for table generation when using the template: `table1` and `DT`. The tables that result from these packages do not work with the auto-numbering and cross-referencing functionality of `bookdown`.

## kableExtra  

```{r kableextra-table}

```

## arsenal  

```{r arsenal-table}

```

## sjPlot  

```{r sjplot-table}

```

# Figures  

There are currently no packages that we recommend or that should be avoided for figure generation.
