---
title: "Tables-Figures-vignette"
output: 
  bookdown::html_document2: 
  base_format: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tables-Figures-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
library(kableExtra)
library(dplyr)
library(arsenal)
library(sjPlot)
library(ggplot2)
```

# Tables

There are three packages I recommend for generating tables: `kableExtra`, `arsenal`, and `sjPlot`.

* `kable` from the `kableExtra` package for printing tables from data frames.
* `tableby` from the `arsenal` package for creating summary tables.
* `tab_model` from the `sjPlot` package for creating HTML tables with model results.  

We are currently aware of two packages that should be avoided for table generation when using the template: `table1` and `DT`. The tables that result from these packages do not work with the auto-numbering and cross-referencing functionality of [bookdown](https://bookdown.org/yihui/rmarkdown-cookbook/cross-ref.html).

## kableExtra  

Use `kable(data.frame)` or pipe a data frame into `kable` to create a table using `kableExtra`. To cross-reference a `kableExrta` table, reference the chunk name (`\@ref(tab:chunk-name)`). An example is shown in Table \@ref(tab:kableextra-table). For more information on using and modifying tables with kableExtra see their [vignette](https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html). 

```{r kableextra-table}
iris |>
  group_by(Species) |>
  summarise("Mean (SD)" = paste0(round(mean(Sepal.Length), 3), " (", 
                                 round(sd(Sepal.Length), 3), ")"),
            "Range" = paste0(round(min(Sepal.Length), 3), " - ", 
                             round(max(Sepal.Length), 3))) |>
  t() |>
  kable(caption = "Summary of sepal length by species.") |>
  kable_styling()
```

## arsenal  

Create a summary table using `arsenal::tableby`. Make sure to set the chunk option `results='asis'` for the results to look nice within the report. To cross-reference a `tableby` object, reference the chunk name (`\@ref(tab:chunk-name)`). An example is show in Table \@ref(tab:arsenal-table). For more information on using `tableby` see their [vignette](https://cran.r-project.org/web/packages/arsenal/vignettes/tableby.html).

```{r arsenal-table, results='asis'}
summary(arsenal::tableby(Species ~ Sepal.Length, data = iris),
        title = "Summary of sepal lengths by species.")
```

The `tableby` vignette says to add `(\\#tab:table-label)` at the beginning of the title in order to reference with `bookdown` but I've found this causes the table to be numbered twice, as seen in table \@ref(tab:tableby-table).

```{r, results='asis'}
summary(arsenal::tableby(Species ~ Sepal.Length, data = iris),
        title = "(\\#tab:tableby-table) Summary of sepal lengths by species.")
```

## sjPlot  

The `tab_model` function from the `sjPlot` package will create an HTML summary table of a model object. To cross-reference a `tab_model` table, add `(\\#tab:table-label)` at the beginning of the title. An example is shown in Table \@ref(tab:sjplot-table). For more information on using `tab_model` see their [vignette](https://strengejacke.github.io/sjPlot/articles/tab_model_estimates.html).

```{r}
sjPlot::tab_model(lm(Sepal.Length ~ Species, data = iris),
                  title = "(\\#tab:sjplot-table) Results of linear regression model.")
```

# Figures  

As of this writing I am not aware of any figure packages that should be avoided. Each figure should be in its own chunk with a figure caption when being printed. As with the `kableExtra` and `tableby` tables, reference the figures using the chunk name (`\@ref(fig:chunk-name)`). Figure \@ref(fig:example-fig) is an example.

```{r example-fig, fig.cap="Boxplot of sepal length by species."}
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() +
  theme_bw()
```

As with the `tableby` table, including `(\\#fig:fig-label)` at the beginning of the figure caption will result in double numbering, as shown in Figure \@ref(fig:example-fig2).

```{r, fig.cap="(\\#fig:example-fig2) Boxplot of sepal length by species."}
ggplot(iris, aes(x = Species, y = Sepal.Length)) +
  geom_boxplot() +
  theme_bw()
```
