---
title: "Template-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Template-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TestPackage)
```

# Introduction  

The CTSC Template provides a skeleton for project documentation and report generation. The template should make it easier to follow reproducible research guidelines and standardize the output for CTSC projects conducted using RStudio.  

# How to use the Template  

* Open a new R Markdown file > From Template > CTSC Biostatistics Template.  
  + Using the template will require you to create a new folder. e.g. CTSC_0000_Investigator.  
* Import and process data.  
  + Cache data if file is large.  
* Run statistical analyses.  
  + Cache analyses if computationally intensive/time consuming.  
* Document data processing steps and analyses.  
* Provide and interpret results for investigator.  

Using the `internal` object in the `setup` chunk we can controll the display/suppression of select sections. `internal=TRUE` will show additional text/results for internal documentation, while `internal=FALSE` will only include sections to send to the investigator.  

# Example  

An example CTSC project using the `iris` data set.  

```{r setup2}
knitr::opts_chunk$set(fig.width=12, fig.height=8,
                      echo=TRUE, warning=FALSE, message=FALSE)

# list default packages to load, add additional packages as necessary
pacman::p_load(dplyr, tidyr, ggplot2, kableExtra, knitr)

# update 'asis' chunk to allow inline code
knit_engines$set(asis = function(options) {
  if (options$echo && options$eval) knit_child(text = options$code)
})


internal <- TRUE
```

```{r source-analyses, include=internal}
# source any external analysis scripts

# if analysis is computationally intensive there are a few options.
#   1) run analysis and save all results to load here
#   2) run analysis here and set chunk option cache=TRUE. A cached chunk will
#      automatically load output and objects from a previous run.
#         see https://bookdown.org/yihui/rmarkdown-cookbook/cache.html for more 
#         information

# check distribution of measurements by group
ggplot(iris, aes(sample = Petal.Length)) +
  geom_qq() +
  geom_qq_line() +
  labs(title = 'Petal Length') +
  facet_wrap(.~Species) +
  theme_bw()
                   
ggplot(iris, aes(sample = Petal.Width)) +
  geom_qq() +
  geom_qq_line() +
  labs(title = 'Petal Width') +
  facet_wrap(.~Species) +
  theme_bw()

ggplot(iris, aes(sample = Sepal.Length)) +
  geom_qq() +
  geom_qq_line() +
  labs(title = 'Sepal Length') +
  facet_wrap(.~Species) +
  theme_bw()
                   
ggplot(iris, aes(sample = Sepal.Width)) +
  geom_qq() +
  geom_qq_line() +
  labs(title = 'Sepal Width') +
  facet_wrap(.~Species) +
  theme_bw()

```


```{r sysinfo, include=internal}
# displays R version, platform, base packages, attached packages, and packages
# loaded via a namespace
sessionInfo()
```

<br>

```{asis, echo=internal}
Data appears to be normally distributed within each species.
```

<br>

# STUDY DESCRIPTION/OBJECTIVE

This study is a brief analysis of the `iris` data set.
 
*Aim 1*: Provide an example of the ctsc_template_short.

*Aim 2*: Investigate the species differences in petal dimensions.

*Aim 3*: Investigate the species differences in sepal dimensions.


# DATA PROCESSING

No data processing was done for this analysis.

# STATISTICAL ANALYSIS

1. Calculate summary statistics for sepal length, sepal width, petal length, and petal width by species.  
2. Test for group differences.


# RESULTS

The group means are provided in Table \@ref(tab:table-demo-kable) and Table \@ref(tab:table-demo-arsenal). As shown in Table \@ref(tab:table-demo-arsenal), all sepal and petal measurements are different between the groups, p < 0.001. A quick look at Figure \@ref(fig:figure-demo) shows that setosa petal length, petal width, and sepal width are likely significantly different from virginica. Sepal length is likely significantly different between setosa and veriscolor.  

For more information on Rmd options please see the Rmd-options-vignette.  
For more information on Tables and Figures please see the Tables-Figures-vignette.  

```{r table-demo-kable, eval=TRUE}
# demo table by piping data into kable()
iris %>%
  group_by(Species) %>%
  summarize(Sepal_Length = paste0(round(mean(Sepal.Length), 2), " \u00B1 ", 
                                  round(sd(Sepal.Length), 2)),
            Sepal_Width = paste0(round(mean(Sepal.Width), 2), " \u00B1 ", 
                                 round(sd(Sepal.Width), 2)),
            Petal_Length = paste0(round(mean(Petal.Length), 2), " \u00B1 ", 
                                  round(sd(Petal.Length), 2)),
            Petal_Width = paste0(round(mean(Petal.Width), 2), " \u00B1 ", 
                                  round(sd(Petal.Width), 2))) %>%
  kable(caption = "Summary of Sepal and Petal Lengths and Widths by Species",
        col.names = c("Species", "Sepal Length", "Sepal Width", "Petal Length", "Petal Width")) %>%
  kable_styling()
```

```{r table-demo-arsenal, eval=TRUE, results='asis'}
summary(arsenal::tableby(Species ~ Sepal.Length + Sepal.Width + Petal.Length +
                           Petal.Width, data = iris, 
                         numeric.stats = c('meansd', 'Nmiss')), 
        pfootnote = TRUE, title = 'Results by Species')
```

```{r figure-demo, fig.cap="\\label{fig:figs}Demo Figure Caption", eval=TRUE}
iris %>%
  pivot_longer(cols = c(Sepal.Length, Sepal.Width, Petal.Length, 
                        Petal.Width),
               values_to = "Measurements", names_to = "Part") %>%
  ggplot(aes(x = Part, y = Measurements, color = Species)) +
  geom_boxplot() + 
  labs(y = "Length or Width (cm)", x = "Plant Part") +
  theme_bw()
```
