---
title: "Project Details"
subtitle: "`r paste0('Date: ', Sys.Date())`"
format:
  html:
    number-sections: true
    toc: true
    toc-location: left
    toc-depth: 3
    embed-resources: true
---

<style type="text/css">

h1.title {
  font-size: 24px;
  font-weight: bolder;
}

h1 { /* Header 1 */
  font-size: 16px;
  font-weight: bold;
}

h2 { /* Header 2 */
  font-size: 14px;
  font-weight: bold;
}

h3 { /* Header 3 */
  font-size: 13px;
  font-weight: bold;
}

h3.subtitle { /* Header 3 Subtitle */
  font-size: 20px;
  font-weight: normal;
  line-height: 150%;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width=12,
  fig.height=8,
  echo=FALSE,
  warning=FALSE,
  message=FALSE
)

# load packages
# pacman::p_load()

# update 'asis' chunk to allow inline code
knitr::knit_engines$set(asis = function(options) {
  if (options$echo && options$eval) knitr::knit_child(text = options$code)
})

```

<hr style="height:1px;color:black;background-color:black">

# INVESTIGATOR

**Name:**

**Department:**

**Contact:**

# RESEARCH QUESTION

Describe the research question(s) that this project aims to address.

# HYPOTHESIS

State the hypothesis or hypotheses for this research project.

# STATISTICAL ANALYSIS PLAN

Provide a brief overview of the statistical methods and approaches that will be used to analyze the data.

## Primary Analysis

Describe the primary statistical analysis methods.

## Secondary Analysis

Describe any secondary or exploratory analyses.

## Sample Size Considerations

If applicable, describe sample size calculations or power analysis.

# TIMELINE

```{r}
#| label: tbl-timeline
#| tbl-cap: "Project Timeline"

# Example timeline table
timeline <- data.frame(
  Milestone = c("Project Kickoff",
                "Data Collection Complete",
                "Data Analysis Complete",
                "Draft Report",
                "Final Report"),
  Target_Date = c("YYYY-MM-DD",
                  "YYYY-MM-DD",
                  "YYYY-MM-DD",
                  "YYYY-MM-DD",
                  "YYYY-MM-DD"),
  Status = c("Not Started",
             "Not Started",
             "Not Started",
             "Not Started",
             "Not Started")
)

kable(timeline,
      col.names = c("Milestone", "Target Date", "Status")) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# PROJECT OUTCOME

Describe the expected outcome or deliverables for this project.

## Expected Deliverables

- Item 1
- Item 2
- Item 3

## Dissemination Plan

Describe plans for publication, presentation, or other dissemination of results.

# PROJECT FILES

```{r}
#| label: tbl-project-files
#| tbl-cap: "Project Files and Locations"

# Table documenting project files and their locations
project_files <- data.frame(
  Project_File = c("Data file name",
                   "Analysis script name",
                   "Results file name"),
  Location = c("/path/to/data/file",
               "/path/to/analysis/script",
               "/path/to/results/file")
)

kable(project_files,
      col.names = c("Project File", "Location")) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Data Dictionary

If applicable, link to or describe the data dictionary for the project.

# NOTES

Additional notes or considerations for the project.
