---
title: "Project Closeout"
subtitle: "`r paste0('Date: ', Sys.Date())`"
format:
  html:
    number-sections: true
    toc: true
    toc-location: left
    toc-depth: 3
    embed-resources: true
---

<style type="text/css">

h1.title {
  font-size: 24px;
  font-weight: bolder;
}

h1 { /* Header 1 */
  font-size: 16px;
  font-weight: bold;
}

h2 { /* Header 2 */
  font-size: 14px;
  font-weight: bold;
}

h3 { /* Header 3 */
  font-size: 13px;
  font-weight: bold;
}

h3.subtitle { /* Header 3 Subtitle */
  font-size: 20px;
  font-weight: normal;
  line-height: 150%;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width=12,
  fig.height=8,
  echo=FALSE,
  warning=FALSE,
  message=FALSE
)

# load packages
# pacman::p_load()

# update 'asis' chunk to allow inline code
knitr::knit_engines$set(asis = function(options) {
  if (options$echo && options$eval) knitr::knit_child(text = options$code)
})

```

<hr style="height:1px;color:black;background-color:black">

# PROJECT INFORMATION

**Project Title:**

**Principal Investigator:**

**Biostatistician:**

**Project Completion Date:**

# PROJECT SUMMARY

Provide a brief summary of the project, including the research question, methods used, and key findings.

# FINAL DATA FILES

```{r}
#| label: tbl-data-files
#| tbl-cap: "Final Data Files and Locations"

# Table documenting final data files and their locations
data_files <- data.frame(
  File_Type = c("Raw Data",
                "Raw Data",
                "Processed Data",
                "Processed Data",
                "Analysis Dataset"),
  File_Name = c("raw_data_file1.csv",
                "raw_data_file2.csv",
                "cleaned_data.csv",
                "merged_data.csv",
                "analysis_ready_data.rds"),
  Location = c("/path/to/raw/data/",
               "/path/to/raw/data/",
               "/path/to/processed/data/",
               "/path/to/processed/data/",
               "/path/to/analysis/data/"),
  Description = c("Original data received from source",
                  "Additional data from secondary source",
                  "Data after cleaning and validation",
                  "Combined dataset from multiple sources",
                  "Final dataset used for analysis")
)

kable(data_files,
      col.names = c("File Type", "File Name", "Location", "Description")) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE) |>
  column_spec(4, width = "30%")
```

## Data Access and Archival

**Data Storage Location:** Describe where the final data is stored (e.g., secure server, cloud storage, institutional repository).

**Data Access:** Describe who has access to the data and any restrictions.

**Retention Period:** Specify how long the data will be retained according to institutional policies.

# CODE AND ANALYSIS FILES

```{r}
#| label: tbl-code-files
#| tbl-cap: "Code and Analysis Files"

# Table documenting code and analysis files
code_files <- data.frame(
  File_Type = c("Data Cleaning Script",
                "Analysis Script",
                "Figure Generation Script",
                "Table Generation Script",
                "Main Report"),
  File_Name = c("01_data_cleaning.R",
                "02_statistical_analysis.R",
                "03_create_figures.R",
                "04_create_tables.R",
                "final_report.qmd"),
  Location = c("/path/to/code/",
               "/path/to/code/",
               "/path/to/code/",
               "/path/to/code/",
               "/path/to/reports/"),
  Description = c("Cleans and validates raw data",
                  "Performs primary and secondary analyses",
                  "Generates all figures for the report",
                  "Creates summary and results tables",
                  "Final Quarto report with all results")
)

kable(code_files,
      col.names = c("File Type", "File Name", "Location", "Description")) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE) |>
  column_spec(4, width = "30%")
```

## Code Repository

**Repository URL:** Link to version control repository (e.g., GitHub, GitLab) if applicable.

**Repository Access:** Describe access permissions and any documentation included in the repository.

# REPORTS AND OUTPUTS

```{r}
#| label: tbl-reports
#| tbl-cap: "Final Reports and Outputs"

# Table documenting reports and outputs
reports <- data.frame(
  Document_Type = c("Final Statistical Report",
                    "Technical Report",
                    "Executive Summary",
                    "Supplementary Materials"),
  File_Name = c("final_report.html",
                "technical_appendix.pdf",
                "executive_summary.docx",
                "supplementary_materials.html"),
  Location = c("/path/to/reports/",
               "/path/to/reports/",
               "/path/to/reports/",
               "/path/to/reports/"),
  Date = c("YYYY-MM-DD",
           "YYYY-MM-DD",
           "YYYY-MM-DD",
           "YYYY-MM-DD")
)

kable(reports,
      col.names = c("Document Type", "File Name", "Location", "Date")) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# PUBLICATIONS AND PRESENTATIONS

## Manuscripts

```{r}
#| label: tbl-manuscripts
#| tbl-cap: "Published or Submitted Manuscripts"

# Table documenting manuscripts
manuscripts <- data.frame(
  Title = c("Manuscript Title 1",
            "Manuscript Title 2"),
  Authors = c("Last, F.M., Last, F.M., et al.",
              "Last, F.M., Last, F.M., et al."),
  Journal = c("Journal Name",
              "Journal Name"),
  Status = c("Published/Submitted/In Preparation",
             "Published/Submitted/In Preparation"),
  DOI_or_Link = c("DOI or URL",
                  "DOI or URL")
)

kable(manuscripts,
      col.names = c("Title", "Authors", "Journal", "Status", "DOI/Link")) |>
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE)
```

## Conference Presentations

```{r}
#| label: tbl-presentations
#| tbl-cap: "Conference Presentations"

# Table documenting conference presentations
presentations <- data.frame(
  Title = c("Presentation Title 1"),
  Presenters = c("Presenter Names"),
  Conference = c("Conference Name"),
  Date = c("YYYY-MM-DD"),
  Type = c("Oral/Poster")
)

kable(presentations,
      col.names = c("Title", "Presenters", "Conference", "Date", "Type")) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Other Dissemination

List any other forms of dissemination (e.g., blog posts, press releases, social media, policy briefs).

# PROJECT COLLABORATORS

**Principal Investigator:** Name, Institution

**Co-Investigators:** Names, Institutions

**Biostatistician(s):** Names, Institution

**Other Contributors:** Names, Roles

# DATA SHARING AND REUSE

**Data Sharing Statement:** Describe any plans for data sharing or public data deposition.

**Data Availability:** If data has been deposited in a public repository, provide the repository name and accession number/DOI.

**Reuse Permissions:** Describe any licenses or restrictions on data reuse.

# LESSONS LEARNED

Document any challenges encountered during the project, lessons learned, and recommendations for future similar projects.

## Methodological Insights

Note any methodological considerations or insights gained during the analysis.

## Workflow Improvements

Suggest any improvements to the workflow or processes for future projects.

# PROJECT CLOSEOUT CHECKLIST

- [ ] All data files archived in appropriate location
- [ ] All code documented and archived
- [ ] Final reports delivered to collaborators
- [ ] Manuscripts submitted or published
- [ ] Data sharing requirements met
- [ ] Authorship and acknowledgments finalized
- [ ] Project files backed up
- [ ] Collaborators notified of project completion

# NOTES

Additional notes or comments regarding project closeout.
